Spatial Relational Models for Neural Circuit Discovery

### 2013-10-21 docs/techreport.tex
added figs

@@

@@

\subsubsection{Normal Distance Fixed Width}
This likeilihood model uses a logistic transform from distance to the
probability $p$ of a connection between two entities $e_i$ and
$e_j$. The latent class component parameters are the center of the
logistic $\mu_{mn}$ and the scale $\lambda_{mn}$. If the distance
between $e_i$ and $e_j$ is less than $\mu_{mn}$ then they are more
likely to be connected. To smooth out the likelihood, we scale the logistic
function by $p_{\textrm{min}}$ and $p_{\textrm{max}}$

@@

>>>>

\DeclareGraphicsRule{.ai}{pdf}{.ai}{}

@@

\begin{figure}
  \centering 
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=\textwidth]{f1.raw.pdf}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}
  \begin{subfigure}[b]{0.55\textwidth}
    \includegraphics[width=\textwidth]{f1.sorted.pdf}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}
\end{figure}

@@

\begin{figure}
  \centering 
  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=0.3\textwidth]{logisticdistance.ai}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}

  \begin{subfigure}[b]{0.4\textwidth}
    \includegraphics[width=0.3\textwidth]{exponentialdistancepoisson.ai}
    \caption{Raw data}
    \label{fig:gull}
  \end{subfigure}

\end{figure}

This likeilihood model uses a logistic transform from distance to the
probability $p$ of a connection between two entities $e_i$ and
$e_j$. The latent class component parameters are the center of the
logistic $\mu_{mn}$ and the scale $\lambda_{mn}$. If the distance
between $e_i$ and $e_j$ is less than $\mu_{mn}$ then they are more
likely to be connected. To smooth out the likelihood, we scale the logistic
function by $p_{\textrm{min}}$ and $p_{\textrm{max}}$

@@

\subsubsection{Normal Distance Fixed witdh}
